The paper on \Large \bf Blockchain Frontrunning

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till section 6

There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}. On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}. Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these DApps. %ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run. 
Here we focus on one ICO that our preliminary research showed that there might be a front-running attack going on. There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.

\subsection{\textit{Status.im} ICO}
As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds. In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the time window for smaller investors. They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.

@@

\subsection{Data Collection and Analysis}
According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started. On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and also potentially failing high gas price transactions.

Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behavior of the participants and miners solely using the default clients nor online blockchain explorers. In order to get the required data, Ethereum blockchain data should be converted to a queryable format. For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}. Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}. A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{github.com / ANONYMOUS}}.

As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards, on gas, while censoring other transactions to the token sale smart contract. The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code flow rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.

@@

Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and take advantage of the monetary profit. The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}. This analysis made us wonder how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?

>>>>

There have been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}. On our DApp samples, there was not ICOs mainly because they tend to run for a short time with a high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}. Needless to say, the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these type of DApps. %ICOs due to the defined cap is similar to our analogy of a queue line, people would line up to get in and there's an opportunity to front-run. 
Here we focus on one ICO that our preliminary research showed that there might have been a front-running incident. There is no doubt that similar behaviour could be seen in other instances of ICOs or similar DApps if investigated.

\subsection{\textit{Status.im} ICO}
As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such an application. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the predefined cap within 3 hours, resulting in close to 300,000 Ether of funds. In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the opprotunity window for smaller investors. They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multi-signature wallet address~\cite{statusicoanalysis}.

@@

\subsection{Data Collection and Analysis}
According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started. On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.

Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behaviour of the participants and miners solely using the default clients nor online blockchain explorers. In order to get the required data, Ethereum blockchain data should be converted to a queryable format. For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{\url{https://cloud.google.com/bigquery/}}. Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{\url{https://www.tableau.com/}}. A copy of this dataset and the initial findings can be found in our Github repository\footnote{\url{github.com / ANONYMOUS}}.

As shown in Figure~\ref{fig:Transactions_miners_while_status_ico_cut}, most of the top miners in the mentioned time frame, have mined almost the same number of failed and successful transactions which were directed toward Status.im token sale, however F2Pool's transactions indicate their successful transactions were equivalent to 10\% of the failed transactions, hence maximizing the mining rewards on gas, while censoring other transactions to the token sale smart contract. The terminology used here is specific to smart contract transactions on Ethereum, by \textit{``failed transaction''} we mean the transactions in which the smart contract code flow rejected and threw an exception and by \textit{``successful transaction''} we mean the transactions that went through and received tokens from the smart contract.

@@

Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions and gain monetary profit. The dataset used for this analysis can be found on our GitHub repository.\footnote{Front-running Status.im ICO dataset: \url{http://github.com/ANONYMOUS}}. 
%______________________________________________________________%
